Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-04-29 stp/paper/main.tex
last change

In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes for the leave-one-out setting.
In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
%This observation provides further evidence of the validity of our new framework.
The first solutions found by \serenepats{} tend to be bigger than those of \serene{}: hence the precision suffers, but the recall is better.
We have further observed that given enough time \serenepats{} finds much better solutions both in precision and recall.

>>>>

In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes for the leave-one-out setting.
In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
The first solutions found by \serenepats{} tend to be bigger than those of \serene{}, hence the precision suffers but the recall is better.
We have also observed that given enough time \serenepats{} finds much better solutions both in precision and recall.
These observations provide further evidence of the validity of our framework.
